Information Distribution Depends on Language-Specific Features

### 2019-01-30 cogsci/position-info.Rmd
bnc

```{r, libraries}
library(png)
library(grid)
library(tidyverse)
library(xtable)
```

@@

```{r switchboard, include=FALSE}
library(feather)

sb_tokens <- read_feather("../switchboard/switchboard.feather") %>%
  mutate(length = str_count(value, " ") + 1) %>%
  mutate(utterance_id = 1:n()) %>%
  unnest_tokens(word, value) %>%
  group_by(utterance_id) %>%
  mutate(word_order = 1:n())

@@

entropies <- map(2:10, ~unigram_entropy(.x, sb_tokens)) %>%
  bind_rows()

ggplot(entropies, aes(x = word_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~ length) + 
  geom_pointrange() +
  geom_smooth(se = F)
```

>>>>

```{r, libraries}
library(png)
library(grid)
library(tidyverse)
library(xtable)
library(tidytext)
library(tidyboot)
library(entropy)
library(here)
library(feather)
```

@@

```{r bnc_and_switchboard, eval = F}
sb_tokens <- read_feather(here("../switchboard/switchboard.feather")) %>%
  mutate(length = str_count(value, pattern = " +") + 1) %>% 
  mutate(utterance_id = 1:n()) %>%
  unnest_tokens(word, value, token = stringr::str_split, pattern = " +") %>%
  group_by(utterance_id) %>%
  mutate(word_order = 1:n())

bnc10_tokens <- read_feather(here("../bnc/bnc10.feather")) %>%
  mutate(word = as.numeric(as.factor(word)))
bnc20_tokens <- read_feather(here("../bnc/bnc20.feather")) %>%
  mutate(word = as.numeric(as.factor(word)))
bnc30_tokens <- read_feather(here("../bnc/bnc30.feather")) %>%
  mutate(word = as.numeric(as.factor(word)))

@@

switchboard_entropies <- map_df(2:10, ~unigram_entropy(.x, sb_tokens))

bnc10_entropies <- unigram_entropy(10, bnc10_tokens)
bnc20_entropies <- unigram_entropy(20, bnc20_tokens)
bnc30_entropies <- unigram_entropy(30, bnc30_tokens)

bnc_entropies <- bind_rows(bnc10_entropies, bnc20_entropies, bnc30_entropies)

write_csv(bnc_entropies, here("data/bnc_entropies.csv"))
write_csv(switchboard_entropies, here("data/switchboard_entropies.csv"))
```

```{r read_bnc_and_switchboard}
bnc_entropies <- read_csv(here("data/bnc_entropies.csv"))
switchboard_entropies <- read_csv(here("data/switchboard_entropies.csv"))
```

```{r plot_bnc_and_switchboard}
ggplot(switchboard_entropies, aes(x = word_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~ length) + 
  geom_pointrange() +
  geom_smooth(se = F)

ggplot(bnc_entropies, aes(x = word_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~ length) + 
  geom_pointrange() +
  geom_line()
```
